Verifying Demonstrations

### 2021-06-17 paper/protocol-untrusted.tex
Clarifications to untrusted protocol

The join procedure is the same, except we add fetching \(t_s\).
So the protester computes \(
  \cid\gets \Hash[\mfst]
\) and \(
  \pid\gets \ACprf[_{\sk_P}][\cid].
\) The protester also fetches a time-correlated random value, \(t_s\), from 
\(\TS\), \(t_s\gets \TSget\).

@@

\daniel{The following should be edited to fit.} 
Note that, thanks to the \((\str,\theta)\)-eligibility criterion
(\cref{DefParticipationCount}), the method of counting is extremely
generic, and each (counting) verifier can make an independent choice to regulate their trust in the final result, based on their initial trust in the witnesses. In other words, anyone who does the counting can choose the eligibility
criteria (time interval, location, number of regular or trusted
witnesses, who is considered to be a trusted witness) for their own count.
As long as \emph{these assumptions/criteria are published along with the 
result}, anyone can verify the correctness of the count under those criteria, 
and potentially question the validity of this choice. Biased or partisan 
verifiers may be tempted to make extreme choices, but they will have to publish 
those choices and lose credibility. Reasonable verifiers on the other hand will 
try to find a good middle-ground that counts all legitimate protesters while 
being resistant to isolated malicious agents.

>>>>

The join procedure is the same, except we add fetching \(t_s\).
So the protester computes \(
  \cid\gets \Hash[\mfst]
\) and \(
  \pid\gets \ACprf[_{\sk_P}][\cid].
\) The protester also fetches a time-correlated random value, \(t_s\), from 
\(\TS\); \(t_s\gets \TSget\).

@@

\daniel{The following should be edited to fit.} 
Note that, thanks to the \((\str,\theta)\)-eligibility criterion
(\cref{DefParticipationCount}), the method of counting is extremely
generic, and each (counting) verifier can make an independent choice to regulate their trust in the final result, based on their initial trust in the witnesses. In other words, anyone who does the counting can choose the eligibility
criteria (time interval, location, number of trusted or untrusted witnesses, 
who is considered to be a trusted witness) for their own count.
As long as \emph{these assumptions/criteria are published along with the 
result}, anyone can verify the correctness of the count under those criteria, 
and potentially question the validity of this choice. Biased or partisan 
verifiers may be tempted to make extreme choices, but they will have to publish 
those choices and lose credibility. Reasonable verifiers, on the other hand, 
will try to find a good middle-ground that counts all legitimate protesters 
while being resistant to isolated malicious agents.
However, what exactly this choice would be is out of scope and, in fact, would 
fall under a different area of research.
